Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-02 paper_jasa.tex
couple more comments

\blue{This gives us a tool to evaluate different types of graphics with respect to their efficiency:} for two different visual test statistics of the same observed data, the one  is better, in which a specific pattern is more easily distinguishable visually. This should be reflected in the power of the test. We can assess power therefore both empirically based on experimental data and through theoretical considerations. Next, we will develop power theoretically and then %It is feasible to assess power theoretically and 
relate it to the empirical results.

>>>>

\blue{This gives us a tool to evaluate different types of graphics with respect to their efficiency:} for two different visual test statistics of the same observed data, the one  is \blue{more efficient}, in which a specific pattern is more easily distinguishable visually. This should be reflected in the power of the test. We can assess power therefore both empirically based on experimental data and through theoretical considerations. Next, we will develop power theoretically and then %It is feasible to assess power theoretically and 
relate it to the empirical results.
